The Geometry of Archaeological Thought: Analysing discplinary change using word embeddings from conference abstracts

### 2020-05-10 documents/paper.Rmd
editing

The data for our study comes from the text of oral and poster presentation abstracts presented at the annual meetings of the Society of American Archaeology (SAA). The earliest meeting in our data is 1962, and we have some years missing, especially 1995-2003. The total number of abstracts is `r abstract_num` (xxx words) from `r year_num` annual meetings. We obtained PDF files of annual programs from https://www.saa.org/annual-meeting/annual-meeting-archives/program-archives.

>>>>

The data for our study comes from the text of oral and poster presentation abstracts presented at the annual meetings of the Society of American Archaeology (SAA). The earliest meeting in our data is 1962, and we have some years missing, especially 1995-2003 where PDF files were not available to us. The total number of abstracts is `r prettyNum(abstract_num, big.mark = ",")` (xxx words) from `r year_num` annual meetings. We obtained PDF files of annual programs from https://www.saa.org/annual-meeting/annual-meeting-archives/program-archives.
